Language-Based Security for Low-Level MPC

### 2024-08-31 ppdp24/slides.tex
checkpoint

  \begin{exampleblock}{Example: 3-Party xor}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \exor\ \sx{2}{2}\ \exor\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$, and therefore either:
  $$
  \sx{1}{1} = 0 \wedge \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \wedge \sx{2}{2} = 0
  $$
  with equal probability. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

  \begin{itemize}
    \item The set of all protocol runs under all possible secrets and random tapes
      induces a probability distribution of program variables.
    \item Conditioning on the output and corrupt secrets =  declassification
      bounds.
    \item Conditioning on adversarial views tells us whether they leak information.
  \end{itemize}

@@

\section{Shamir Addition}
\begin{frame}{Secret Sharing}

  To implement 3-party summation (xor in $\mathbb{F}_2)$, we can use \emph{Shamir addition}.
  Each party first generates \emph{reconstructive shares}.

@@

\begin{frame}{Public Reveal}

@@

\begin{frame}{Output}

@@

>>>>

  \begin{exampleblock}{Example: 3-Party xor}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \exor\ \sx{2}{2}\ \exor\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$, and therefore either:
  $$
  \sx{1}{1} = 0 \wedge \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \wedge \sx{2}{2} = 0
  $$
  with \cemph{equal probability of .5}. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

  \begin{itemize}
    \item The set of all protocol runs under all possible secrets and random tapes
      induces a probability distribution of program variables.
    \item Conditioning on the output and corrupt secrets =  declassification
      bounds.
    \item Conditioning on adversarial views tells us whether they leak information--
      if it changes the distribution of honest secrets.
  \end{itemize}

@@

\section{Example: Shamir Addition}
\begin{frame}{Example: Shamir Addition}

  To implement 3-party summation (xor in $\mathbb{F}_2$), we can use \emph{Shamir addition}.
  Each party first generates \emph{reconstructive shares}.

@@

\begin{frame}{Example contd.: Public Broadcast Reveal}

@@

\begin{frame}{Example contd.: Output}

@@

  %\begin{exampleblock}{Example Bad Protocol}
  %  If 1 is honest and accidentally broadcasts its local share:
  %  $$
  %  \mx{leak}{*} := \elab{\locflip}{1}
  %  $$
  %  conditioning on adversarial views now yields probability 1 for
  %  either $\sx{1}{1} = 0 \wedge \sx{2}{2} = 1$ or
  %  $\sx{1}{1} = 1 \wedge \sx{2}{2} = 0$.
  %\end{exampleblock}
